Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-09 sas2015/content/impl.tex
text squeezing pass througth section 4

\section{Correlated Calls Analysis}\label{sec:cca}
The correlated-calls analysis is defined as a transformation from an arbitrary IFDS problem to a corresponding IDE problem. The solution of this IDE problem can be converted to a solution of the original IFDS problem. The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
converts it into an equivalent IDE problem. We consider two transformations:
\begin{itemize}
    \item an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
    \item a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
\end{itemize}
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

@@

%\paragraph{Converting IFDS problems to IDE problems}
%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
The lattice
for the equivalence transformation $\transEq$ 
is the two-point lattice
    $L^\equiv=\{\bot,\ \top\}$,
where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
The edge functions $\edgefn^\equiv$ are defined as
\begin{equation}
    \edgefn^\equiv=
    \begin{cases}
        \lambda e\,.\,\lambda m\,.\,\bot&\text{if $e=(n_1,\mathbf0)\to(n_2,d_2)$, where $d_2 \neq \mathbf0$;}\\
      \lambda e\,.\,\id&\text{otherwise.}
    \end{cases}
\end{equation}
At a~``diagonal'' edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact
$d$, the micro function returns $\bot$
to make
the fact $d$ reachable. All other micro-functions are the identity function.
%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
The equivalence transformation is thus defined as:
  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.

@@

We can now define $\edgefn$, which assigns a micro-function to each edge in
the exploded supergraph. 
Along a $\mathbf0$-edge, the micro function is the identity. 
All other functions can be described with $\varepsilon_S$.
On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to the initial
map $\botcc$ that conservatively allows every receiver to point to an object of any type.
On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
The is formalized in the following definition.
\begin{definition}\label{def:edgefn}
For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
  \begin{equation}\label{eq:edgefndef}
      \ccedgefn S(e)=
        \begin{cases}
          \id  &\text{if $d_1=d_2=\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
        \end{cases}
  \end{equation}
  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
\end{definition}

\begin{example}
  Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.

  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $r$ to \code v.

Similarly, on the call-start edge from \code{main} to \code{B.bar}, the possible types
of the receiver \code{a} are further restricted by the micro-function
$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
on the edge that passes the argument \code{v} to the parameter \code{s}.

The composition of these micro functions results in the empty set as the possible
types of the receiver \code{a}, indicating that this data-flow path that would
result in an information leak is actually infeasible.
\end{example}

@@

Finally, the correlated-calls transformation is defined as
    \begin{equation}
      \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right).
    \end{equation}

@@

For each program point $n$, the result of an IFDS analysis gives
a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
pairs each such fact~$d$ with a lattice element $\ell$. Formally,
for an IFDS problem $P$, the result $\resultIFDS$ has type
$N^* \to D$.
Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
has type $N \to (D \to L)$.

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}

%\otodo{I don't understand this comment. What does it mean?}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
\end{equation}
%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
%    the original was incorrect. Marianna, please check that this correction is correct.}

@@

Conceptually, micro-functions are functions from $L$ to $L$, where $L$
is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. However,
the IDE algorithm requires an efficient representation of micro-functions.
The chosen representation needs to support the basic micro-functions that
we presented in Section~\ref{seq:transIfdsIde}. The representation must also
support function application, comparison, and be closed under function composition
and meet. We now propose such a representation for the correlated-calls micro-functions.

The representation of a micro-function is a map from receivers to pairs of sets of
types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. 
Intuitively, the micro-function takes the existing set of possible types of the
receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$.
We use the notation
$\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
sets corresponding to a particular receiver $r$. We define the meaning $\denote{\setpair{I}{U}}$
of a representation $\setpair{I}{U}$ as follows: $\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
from receivers to sets of types, and returns a map that maps each receiver $r$ to
the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
with $U(r)$.

All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
in this representation.

The implementation of function application follows directly from the definition of
the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
%\mtodo{Should this be the denotation of $\setpair IU$?}
%\otodo{No. It is an implementation of the apply operation.}

To compare two micro-functions for equality, it suffices to compare the corresponding
sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
implementation of comparison corresponds to equality of the represented micro-functions:
\begin{restatable}{lemma}{equalEq}
\label{lem:equalEq}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \begin{equation}
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
    \end{equation}
\end{restatable}
The proofs of all of the lemmas and theorems are in the Appendix.

The following lemma shows that this implementation corresponds to the composition
of the denoted functions.
\begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}},
    \]
    where the composition of two micro-function representations is defined as follows:
$$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}.$$
\end{restatable}

The following lemma shows that this implementation corresponds to the meet
of the denoted functions:
\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
\label{lem:equalMeet}
    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \begin{equation}
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
    \end{equation}
    where the meet of two micro-function representations is defined as follows:
$$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}.$$
\end{restatable}

@@

In the following lemma we show that our analysis is sound, i.e. that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.

@@

We next show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.

@@

\begin{definition}
Let $c_1$ and $c_2$ be two call sites on a receiver $r\in R$.
  If both call sites are polymorphic, then we say that $r$ is a \textit{correlated-call receiver}.
\end{definition}
In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
We will denote the set of correlated-call receivers as $\rcc$.

We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$. We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.

@@

To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.

@@

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
so this running time must be multiplied by the cost of evaluating a
micro-function. We show that the micro-functions in the correlated-calls
IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
is $O(ED^3\rcc T)$.

Specifically, the complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove these conditions with the following lemma:
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient and the required operations
  on micro-functions can be computed in time $O(\rcc T)$.
\end{restatable}

@@

\subsection{Implementation of the Correlated-Calls Analysis}
The correlated-calls analysis was implemented in the Scala programming language~\cite{odersky2004overview}. 
The input programs that we analyzed were written in Java. Our implementation analyzed the
corresponding Java bytecode.
To retrieve information about an input program, such as its control-flow supergraph or the set of receivers and their types, we used the WALA framework~\cite{fink2012wala}.
Since WALA currently only contains an implementation of IFDS, we implemented IDE from scratch. Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

@@

The artifact of our implementation can be used to solve any IFDS problem. In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.

>>>>

\section{Correlated Calls Analysis}\label{sec:cca}
%The correlated-calls analysis is a transformation from an arbitrary IFDS problem to a corresponding IDE problem. The solution of this IDE problem can be converted to a solution of the original IFDS problem. The converted IFDS result can be more precise than the original IFDS result because it avoids infeasible paths corresponding to correlated calls.

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
Let $G^\#$ be the exploded supergraph of an arbitrary IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,L,\,\edgefn)$
converts the IFDS problem into an IDE problem.
We consider two IFDS-to-IDE transformations: an \textit{equivalence transformation} $\transEq$ (pronounced ``t-equiv'') and
a \textit{correlated-calls transformation} $\transCC$ (pronounced ``t-c-c'').
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
The solution of the IDE problem
can be mapped back to an IFDS solution.
If the equivalence transformation was used, then this solution is identical to the
solution that would be computed by the IFDS algorithm for the original IFDS problem.
If the correlated-calls transformation was used, then this solution is more precise
because it excludes flow along infeasible paths due to correlated calls.

%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

@@

%\paragraph{Converting IFDS problems to IDE problems}
%Since IDE is a generalization of IFDS, any IFDS problem can be converted into an equivalent IDE problem~\cite{sagiv1996precise}.
The lattice
for the equivalence transformation $\transEq$ 
is the two-point lattice
    $L^\equiv=\{\bot,\ \top\}$,
where $\bot$ means ``reachable'', and $\top$ means ``not reachable''. 
The edge functions $\edgefn^\equiv$ are defined as
\begin{equation}
    \edgefn^\equiv=
    \begin{cases}
        \lambda e\,.\,\lambda m\,.\,\bot&\text{if $e=(n_1,\mathbf0)\to(n_2,d_2)$, where $d_2 \neq \mathbf0$;}\\
      \lambda e\,.\,\id&\text{otherwise.}
    \end{cases}
\end{equation}
At a~``diagonal'' edge from a $\mathbf0$-fact to a non-$\mathbf0$-fact
$d$, the micro function returns $\bot$
to make
the fact $d$ reachable. All other micro-functions are the identity function.
%\mtodo{``the identity function'' or is it okay ot just say ``the identity''?}.
\commentout{
The equivalence transformation is thus defined as:
  $\transEq((G^\#))=(G^\#,\,L^\equiv,\,\mathsf{EdgeFn}^\equiv)$.
}

@@

We can now define $\edgefn$, which assigns a micro-function to each edge in
the exploded supergraph. 
Along a $\mathbf0$-edge, the micro function is the identity. 
%All other functions can be described with $\varepsilon_S$.
On a ``diagonal'' edge from $\mathbf0$ to a non-$\mathbf0$ fact that corresponds
to some data-flow fact becoming reachable, $\varepsilon_S(e)$ is applied to
%the initial map
$\botcc$ that maps every receiver to an object of every possible type.
%conservatively allows every receiver to point to an object of any type.
On all other edges, $\varepsilon_S(e)$ is applied to the existing map before the edge.
The is formalized in the following definition.
\begin{definition}\label{def:edgefn}
For each edge $e = (n_1,d_1) \to (n_2,d_2)$, $\ccedgefn S(e)$ is defined as follows:
  \begin{equation}\label{eq:edgefndef}
      \ccedgefn S(e)=
        \begin{cases}
          \id  &\text{if $d_1=d_2=\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(\botcc) &\text{if $d_1=\mathbf0$ and $d_2\ne\mathbf0$},\\
          \lambda m\,.\,\varepsilon_S(e)(m)  &\text{otherwise.}
        \end{cases}
  \end{equation}
  %We define both $\ccedgefn S$ and $\varepsilon_S$ to be extended to paths by composition.
\end{definition}

\begin{example}
  Consider the program from Figure~\ref{list:ccexample}, whose exploded supergraph appeared in Figure~\ref{fig:cc_edgefn_example}.
%
  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\mathbf0$-fact to the method's return value $r$. 
  The diagonal edge is labeled with $\lambda m\,.\,\botcc$, so every receiver is mapped to the set of all types~$\bot_T$.
%  
On the end-return edge from \code{A.foo} to \code{main}, the set of types of \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ corresponding to the assignment of the return value $r$ to \code v.
%
%Similarly,
On the call-start edge from \code{main} to \code{B.bar}, the possible types
of \code{a} are further restricted by the micro-function
$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
on the edge that passes the argument \code{v} to the parameter \code{s}.
The composition of these micro functions results in the empty set as the possible
types \code{a}, indicating that this
%data-flow
path 
%that would
%result in an information leak 
is 
%actually
infeasible.
\end{example}

@@

\commentout{
Finally, the correlated-calls transformation is defined as
    \begin{equation}
      \transCC_S((G^\#))=\left(G^\#,\,\lcc_S,\,\ccedgefn S\right).
    \end{equation}
}

@@

An IFDS solution $\resultIFDS$ has type $N^* \to D$: it maps each program point $n$
to a set of facts $d$ that may be reached at $n$.
\otodo{This seems wrong: Why is it $N^*$ for IFDS and $N$ for IDE? And shouldn't
    it be $N \to 2^D$, since you get a set of $d$'s?}
An IDE solution $\resultIDE$
pairs each such fact~$d$ with a lattice element $\ell$, so its type
is $N \to (D \to L)$.

%For each program point $n$, the result of an IFDS analysis gives
%a set of facts $d$ that may be reached at $n$. The result of an IDE analysis
%pairs each such fact~$d$ with a lattice element $\ell$. Formally,
%for an IFDS problem $P$, the result $\resultIFDS$ has type
%$N^* \to D$.
%Similarly, for an IDE problem $Q$, the result $\resultIDE(Q)$
%has type $N \to (D \to L)$.

In the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, an IDE solution $\rho$ computed using $\transEq$ is converted to
and IFDS solution as:
  $\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}$.
%a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
%is converted to an IFDS result as follows:
%\begin{equation}\label{eq:transEqDef}
  %\backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
%\end{equation}
%
%\otodo{I don't understand this comment. What does it mean?}
%
In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data-flow path is
infeasible. Therefore, an IDE solution $\rho$ computed using
$\transCC_S$ is converted to an IFDS solution as:
$\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}$.

%a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
%converted to an IFDS result as follows:
%\begin{equation}\label{eq:transCcDef}
    %\backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
%\end{equation}
%\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
%    the original was incorrect. Marianna, please check that this correction is correct.}

@@

Conceptually, micro-functions are functions from $L$ to $L$, where $L$
is the IDE lattice, either $L^\equiv$ or $\lcc$ in our context. 
The IDE algorithm requires an efficient representation of micro-functions.
The chosen representation needs to support the basic micro-functions that
we presented in Section~\ref{seq:transIfdsIde}, and it must
support function application, comparison, and be closed under function composition
and meet. We now propose such a representation for the correlated-calls micro-functions.

The representation of a micro-function is a map from receivers to pairs of sets of
types $I(r)$ and $U(r)$, where $U(r)$ is required to be a subset of $I(r)$. 
We use the notation
$\setpair{I}{U}$ to represent such a map, and $I(r)$ and $U(r)$ to look up the
sets corresponding to a particular receiver $r$.
The micro-function takes the existing set of possible types of the
receiver $r$, intersects it with $I(r)$, then unions it with $U(r)$:
$\denote{\setpair{I}{U}} = \lambda m\,.\,\lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.

%We define the meaning $\denote{\setpair{I}{U}}$
%of a representation $\setpair{I}{U}$ as follows: 
%In words, the micro-function represented by $\setpair{I}{U}$ takes an existing map $m$
%from receivers to sets of types, and returns a map that maps each receiver $r$ to
%the set $m(r)$ given by the original map $m$ intersected with $I(r)$ and unioned
%with $U(r)$.

All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
in this representation. The following lemmas show how function comparison, composition, and meet can be implemented using basic set operations
on $I$ and $U$.
The proofs of all of the lemmas and theorems are in the Appendix.

%The implementation of function application follows directly from the definition of
%the representation: $\setpair{I}{U}(m) = \lambda r\,.\,(m(r) \cap I(r)) \cup U(r)$.
%\mtodo{Should this be the denotation of $\setpair IU$?}
%\otodo{No. It is an implementation of the apply operation.}

%To compare two micro-functions for equality, it suffices to compare the corresponding
%sets $I(r)$ and $U(r)$ for all receivers $r$. The following lemma shows that this
%implementation of comparison corresponds to equality of the represented micro-functions:
\begin{restatable}{lemma}{equalEq}
\label{lem:equalEq}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \begin{equation}
        \forall r\,.\,I(r) = I'(r) \land U(r) = U'(r)
        \iff
        \denote{\setpair{I}{U}} = \denote{\setpair{I'}{U'}}.
    \end{equation}
\end{restatable}

%The following lemma shows that this implementation corresponds to the composition
%of the denoted functions.
\begin{restatable}{lemma}{equalComp}\label{lem:equalComp}
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \[
        \denote{\setpair{I}{U} \circ \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \circ \denote{\setpair{I'}{U'}},
    \]
    where the composition of two micro-function representations is defined as follows:
$$\setpair{I}{U} \circ \setpair{I'}{U'} = \setpair{\lambda r\,.\,(I(r) \cap I'(r))\cup U(r)}{\lambda r\,.\,(I(r)\cap U'(r))\cup U(r)}.$$
\end{restatable}

%The following lemma shows that this implementation corresponds to the meet
%of the denoted functions:
\begin{restatable}{lemma}{equalMeet}\label{lem:equalMeet}
\label{lem:equalMeet}
    Let $\denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}}
     =\lambda m.\lambda r.\denote{\setpair{I}{U}}(m)(r)\cup\denote{\setpair{I'}{U'}}(m)(r)$.
    For any pair of micro-function representations $\setpair{I}{U}$, $\setpair{I'}{U'}$,
    \begin{equation}
        \denote{\setpair{I}{U} \sqcap \setpair{I'}{U'}}
        = 
        \denote{\setpair{I}{U}} \sqcap \denote{\setpair{I'}{U'}},
    \end{equation}
    where the meet of two micro-function representations is defined as follows:
$$\setpair{I}{U} \sqcap \setpair{I'}{U'} = \setpair{\lambda r\,.\,I(r) \cup I'(r)}{\lambda r\,.\,U(r) \cup U'(r)}.$$
\end{restatable}

@@

The following lemma shows that our analysis is sound, i.e. 
that the resulting IDE problem still considers all data-flow
paths that are actually feasible.
%that the result of an IDE problem obtained through a correlated-calls transformation removes only facts that occur on infeasible paths.

@@

We also show that the result of an IDE problem obtained through a correlated-calls transformation is a subset of the original IFDS result.

@@

\begin{definition}
    If $r\in R$ is the receiver of at least two polymorphic
    call sites, then we call $r$ a \textit{correlated-call receiver}, and we define $\rcc$ as the set of all
  such receivers.
\end{definition}
%In other words, a correlated-call receiver is a receiver that has at least two polymorphic call invocations.
%We will denote the set of correlated-call receivers as $\rcc$.

We will show that it is sufficient for the correlated-calls
micro-functions to be defined only on correlated-call receivers.
%We will describe a ``reduced'' correlated-calls transformation in which we only consider receivers from $\rcc$ and ignore other receivers of $R$.
Specifically, a ``reduced'' correlated-calls transformation that
considers only correlated-call receivers in the micro-functions
yields the same solution as the full correlated-calls transformation
(i.e. no precision is lost).
%We will show that IDE problems obtained through ordinary and reduced correlated-calls transformations yield the same results.
%In other words, we show that if a correlated-calls analysis considers only correlated-call receivers, no precision is lost.

@@

\commentout{
To summarize, Lemma~\ref{lem:sound} shows that the result of a correlated-calls analysis is sound since it overapproximates the data flow of all possible concrete execution paths.
We have also shown in Lemma~\ref{lem:subsetifds} that for an IFDS problem $P$, the correlated-calls analysis improves the precision of the original IFDS result $\resultIFDS(P)$, because the correlated-calls result $\resultIDE(\transCC(P))$ underapproximates an equivalence-IDE result $\resultIDE(\transEq(P))$.
Finally, we showed in Lemma~\ref{lem:onlycorrrec} that a correlated-call transformation to IDE that considers only correlated-call receivers $\rcc$ achieves the same result that is obtained when considering all receivers $R$.
}

@@

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
so this running time must be multiplied by the cost of evaluating a
micro-function. We show that the micro-functions in the correlated-calls
IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
is $O(ED^3\rcc T)$. Note that in practice, $\rcc$ is much smaller
than $R$, so Lemma~\ref{lem:onlycorrrec} is significant for 
performance.

Specifically, the complexity proof for the IDE algorithm requires
the implementation of the micro-functions to be \textit{efficient}
according to a list of specific criteria. Our micro-function
implementation does satisfy the criteria:

\otodo{Give the list of criteria explicitly in the proof in the appendix.}
%\begin{enumerate}
	%\item There is a representation for the identity and top functions.
  %\item The representation is closed under the meet and composition operations.
  %\item The micro functions form a finite-height lattice.
  %\item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  %\item There is a constant bound on the storage space for a micro function representation.
%\end{enumerate}
%We prove these conditions with the following lemma:
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient and the required operations
  on micro-functions can be computed in time $O(\rcc T)$.
\end{restatable}

@@

\subsection{Implementation of the Correlated-Calls Analysis}
We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzed Java bytecode from input programs written
in Java.
%The input programs that we analyzed were written in Java. Our implementation analyzed the
%corresponding Java bytecode.
We used WALA~\cite{fink2012wala}
to retrieve information about an input program, such as its control-flow supergraph and the set of receivers and their types.
Since WALA does contain an implementation of the IDE algorithm,
we implemented it from scratch.
%currently only contains an implementation of IFDS, we implemented IDE from scratch.
We will submit our implementation to the artifact evaluation committee, and we are working on contributing it officially to WALA. % Instead of using WALA's IFDS implementation, to run an IFDS problem, we converted it to an IDE problem and used our own IDE solver.

@@

\commentout{
The artifact of our implementation can be used to solve any IFDS problem. In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
}
